---
title: "WebMD Doctors Virginia"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(RSelenium)
library(rvest)
library(data.table)
# devtools::install_github("dads2busy/dataplumbr")
library(dataplumbr)
library(dplyr)
library(tibble)
library(tidygeocoder)
library(iterators)
library(itertools)
library(magrittr)
library(sf)
source("../../src/helper_functions.R")
```

## Create Remote Driver for Selenium
```{r}
# IF ON RIVANNA, USE THIS
# There are four instances of Selenium currently running on our server, each with a different port number.
# Set the port you want to use (4444, 4445, 4446, or 4447) and run your code.
# To monitor what is going on, a separate port is available for each of the selenium instances (7900, 7901, 7902, 7903). Password is 'secret'.

port <- 4444
ip <- Sys.getenv("OSRM_SERVER")
rdBrowser <- "firefox"

remDr <- remoteDriver$new(
  remoteServerAddr = ip,
  port = port,
  browserName = rdBrowser
)

remDr$open()
remDr$setTimeout(type = "page load", milliseconds = 20000)
# remDr$navigate("http://www.google.com/ncr")
# remDr$navigate("http://www.r-project.org")

# IF ON LOCAL COMPUTER< USE THIS
# rD <- rsDriver(browser="firefox", port=4599L, verbose=F)
# remDr <- rD[["client"]]
# remDr$setTimeout(type = "page load", milliseconds = 20000)
```

## Create a function for getting doctor cards within 100 miles of given point
```{r}
# For each of these:
"pt=37.5537,-77.4602&city=Richmond&state=VA"
"pt=37.2709,-79.9414&city=Roanoke&state=VA"
"pt=36.9533,-81.0872&city=Wytheville&state=VA"
"pt=36.6929,-77.5444&city=Emporia&state=VA"
"pt=37.2557,-76.0084&city=Cape Charles&state=VA"
"pt=38.3031,-77.4605&city=Fredericksburg&state=VA"
"pt=38.4495,-78.8689&city=Harrisonburg&state=VA"

# Create function:
get_page <- function(page_num = 1) {
  remDr$navigate(paste0("https://doctor.webmd.com/results?q=Primary%20Care&sids=29277,29264,29259&pagenumber=", page_num, "&d=161&rd=161&sortby=bestmatch&medicare=false&medicaid=false&newpatient=false&isvirtualvisit=false&minrating=0&pt=38.4495,-78.8689&city=Harrisonburg&state=VA"))
}
```

## Additonal Functions for 1) Getting a doctor card, and 2) Getting the info from the doctor card
```{r}
get_dr_cards <- function(remDr) {
  page <- remDr$findElements(using = "xpath", value = "//*[@class = 'card-info-wrap']")
  data.frame(link = unlist(sapply(page, function(x){x$getElementAttribute('innerHTML')[[1]]})))
}

get_dr_info <- function(html) {
  dr_name <- html %>% rvest::html_nodes(css = "h2") %>% rvest::html_text()
  dr_specs <- html %>% rvest::html_nodes(css = ".prov-specialty") %>% rvest::html_text()
  dr_addr <- html %>% rvest::html_nodes(css = ".addr-text") %>% rvest::html_text() %>% trimws(., "both")
  data.table(name = dr_name, specialties = dr_specs, address = dr_addr)
}
```

## For each page of doctor cards run this loop
You'll need to get the final page number by looking at the bottom of the first page
```{r}
dr_info_dt <- data.table(name = character(), specialties = character(), address = character())
for (p in 1:5) {
  Sys.sleep(1)
  print(p)
  get_page(page_num = p)
  dr_cards <- get_dr_cards(remDr)
  if (!is.null(dr_cards)) {
    for (i in 1:nrow(dr_cards)) {
      if (!is.null(dr_cards$link[i])) {
        html <- read_html(dr_cards$link[i])
        dr_info <- get_dr_info(html)
        dr_info_dt <- rbindlist(list(dr_info_dt, dr_info))
      }
    }
  }
}
```

## Write out to csv file
```{r}
readr::write_csv(dr_info_dt, "data/doctor_pages/doctor_pages_harrisonburg_1_1278.csv")
```

## Close Selenium Connection
```{r}
remDr$close()
```

## Upload All CSV Files to Database
```{r}
file_paths <- list.files("data/doctor_pages", full.names = T)

for (i in 1:length(file_paths)) {
  dt <- fread(file_paths[i])
  dbWriteTable(con, c("data_commons", "virginia_primary_care_doctors"), dt, overwrite = F, append = T, row.names = F)
}

dbDisconnect(con)
```

## Remove Duplicate Records from Database Table; make owner data_commons
```{r}
con <- get_db_conn(db_host = "localhost", db_port = 5434)
dbSendQuery(con, "SELECT DISTINCT * INTO data_commons.virginia_primary_care_doctors_unq FROM data_commons.virginia_primary_care_doctors")
dbSendQuery(con, "DROP TABLE data_commons.virginia_primary_care_doctors")
dbSendQuery(con, "ALTER TABLE data_commons.virginia_primary_care_doctors_unq RENAME TO virginia_primary_care_doctors")
dbSendQuery(con, "ALTER TABLE data_commons.virginia_primary_care_doctors OWNER TO data_commons")
dbDisconnect(con)
```

## Geocode All Doctor Addresses and Write to Database
```{r}
con <- get_db_conn()
test_records <- dbGetQuery(con, "SELECT * FROM data_commons.virginia_primary_care_doctors")
dbDisconnect(con)

test_addrs <- unique(as_tibble(test_records[, c("name", "address")]))

# geocode the addresses
lat_longs <- test_addrs[30001:44128,] %>%
  geocode(address, 
          method = 'google',
          lat = latitude , 
          long = longitude, 
          full_results = FALSE)

con <- get_db_conn()
dbWriteTable(con, c("data_commons", "virginia_primary_care_doctors_geolocated"), lat_longs, overwrite = F, append = T, row.names = F)
dbDisconnect(con)
```

## Reverse Geocode to Add Census Geographies using FCC API
```{r}
con <- get_db_conn()
va_docs <- dbGetQuery(con, "SELECT * FROM data_commons.virginia_primary_care_doctors_geolocated")
dbDisconnect(con)

# add unique id column
va_docs$id <- 1:nrow(va_docs) 

va_docs_sample <- va_docs[1:10,]

ic <- ichunk(1:nrow(va_docs), 500)

it <- iter(va_docs, by = "row", chunksize = 10)

for (i in 1:nrow(va_docs)) {
  locs <- loc.lat_lon2geo_areas(place_id = va_docs$id[i], lat = va_docs$latitude[i], lon = va_docs$longitude[i])
  Sys.sleep(0.5)
  if (exists("locs_dt")) {
    locs_dt <- rbindlist(list(locs_dt, locs))
  } else {
    locs_dt <- locs
  }
}
```

## Get census blocks by st_intersect with Virginia and surrounding state block maps
```{r}

con <- get_db_conn() 
docs <- dbGetQuery(con, "select * from data_commons.virginia_primary_care_doctors_geolocated")
dbDisconnect(con)
  
docs_sf <- st_as_sf(docs[!is.na(docs$latitude) & !is.na(docs$longitude),], coords = c("longitude", "latitude"), crs=4326)

blk_map_path_51 <- paste0("/home/ads7fg/sdad/projects_data/usda/bb/original/censusblocks/blocks_TIGER2018_sf_RDS/tl_2018_51_tabblock10.RDS") 
blk_map_path_54 <- paste0("/home/ads7fg/sdad/projects_data/usda/bb/original/censusblocks/blocks_TIGER2018_sf_RDS/tl_2018_54_tabblock10.RDS")
blk_map_path_37 <- paste0("/home/ads7fg/sdad/projects_data/usda/bb/original/censusblocks/blocks_TIGER2018_sf_RDS/tl_2018_37_tabblock10.RDS")
blk_map_path_24 <- paste0("/home/ads7fg/sdad/projects_data/usda/bb/original/censusblocks/blocks_TIGER2018_sf_RDS/tl_2018_24_tabblock10.RDS")
blk_map_path_11 <- paste0("/home/ads7fg/sdad/projects_data/usda/bb/original/censusblocks/blocks_TIGER2018_sf_RDS/tl_2018_11_tabblock10.RDS")
blk_map_path_47 <- paste0("/home/ads7fg/sdad/projects_data/usda/bb/original/censusblocks/blocks_TIGER2018_sf_RDS/tl_2018_47_tabblock10.RDS")
blk_map_path_42 <- paste0("/home/ads7fg/sdad/projects_data/usda/bb/original/censusblocks/blocks_TIGER2018_sf_RDS/tl_2018_42_tabblock10.RDS")
blk_map_path_21 <- paste0("/home/ads7fg/sdad/projects_data/usda/bb/original/censusblocks/blocks_TIGER2018_sf_RDS/tl_2018_21_tabblock10.RDS")

blk_map_51 <- readRDS(blk_map_path_51)  
blk_map_54 <- readRDS(blk_map_path_54) 
blk_map_37 <- readRDS(blk_map_path_37) 
blk_map_24 <- readRDS(blk_map_path_24) 
blk_map_47 <- readRDS(blk_map_path_47) 
blk_map_42 <- readRDS(blk_map_path_42) 
blk_map_21 <- readRDS(blk_map_path_21) 
blk_map_11 <- readRDS(blk_map_path_11)
blk_map_11$STATEFP <- NULL
blk_map_11$COUNTYFP <- NULL

blk_map <- bind_rows(list(blk_map_11, blk_map_21, blk_map_24, blk_map_37, blk_map_42, blk_map_47, blk_map_51, blk_map_54)) %>% sf::st_transform(4326)

int <- sf::st_intersects(docs_sf, blk_map) 
int2 <- as.integer(as.character(int)) 
docs_sf$geoid_blk <- as.character(blk_map$GEOID10[unlist(int2)]) 
```

## Upload to Database
```{r}
con <- get_db_conn() 
st_write(docs_sf, con, c("data_commons", "virginia_primary_care_doctors_geolocated_blks"))
dbDisconnect(con)
```

## Change table owner
```{r}
con <- get_db_conn() 
dbSendQuery(con, "ALTER TABLE data_commons.virginia_primary_care_doctors_geolocated_blks OWNER TO data_commons")
dbDisconnect(con)
```

## Remove Duplicates
```{r}
con <- get_db_conn()
dbSendQuery(con, "SELECT DISTINCT * INTO data_commons.virginia_primary_care_doctors_geolocated_blks_unq FROM data_commons.virginia_primary_care_doctors_geolocated_blks")
dbSendQuery(con, "DROP TABLE data_commons.virginia_primary_care_doctors_geolocated_blks")
dbSendQuery(con, "ALTER TABLE data_commons.virginia_primary_care_doctors_geolocated_blks_unq RENAME TO virginia_primary_care_doctors_geolocated_blks")
dbSendQuery(con, "ALTER TABLE data_commons.virginia_primary_care_doctors_geolocated_blks OWNER TO data_commons")
dbDisconnect(con)
```

